Network segregation, Social Isolation and Preference for Redistribution across societies

### 2023-09-29 paper.Rmd
pdf

---
title: "Network segregation, Social Isolation and Preference for Redistribution across societies"
css: "input/css/custom.css" # custom CSS para html
linestretch: '1.5'          # interlineado 
link-citations: yes         # citas linkeadas
# date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
date: "`r format(Sys.Date(), '%d %B %Y')`"
author:
# - name: Julio Iturra-Sanhueza
#   affiliation: University of Bremen
#   email: jiturra@uni-bremen.de
#   number: 1
# - name: Justin d'Ottawa
#   affiliation: University of Ottawa
#   number: 2
# - name: Pedro Torres
#   number: 1,2 
# Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
# abstract: "Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do *eiusmod tempor* incididunt ut labore et dolore magna aliqua. Ut enimad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat."
output:
  bookdown::html_document2:
    toc: yes
    code_folding: hide
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false   
  bookdown::pdf_document2:
    template: null
    toc: false
    keep_tex: false
    pandoc_args:
      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
linkcolor: blue                         # enlaces y citas en color azul
bibliography: input/bib/rgroup-redist.bib     # bibliografia en bibtex
csl: input/bib/apa6.csl
editor_options:
  chunk_output_type: console            # en RStudio, mostrar output en consola
geometry: "left=2cm,right=2cm,top=3cm,bottom=3cm" # márgenes de página
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
---

@@

The response categories are  (1)"Never", (2)"Rarely", (3) "Sometimes", (4)"Often" and  (5)"Very often". As the indicators show an acceptable internal consistency (α=.85), an index of the three items was created. Positive values indicate higher perceived isolation.

>>>>

---
title: "Network segregation, Social Isolation and Preference for Redistribution across societies"
css: "input/css/custom.css" # custom CSS para html
linestretch: '1.5'          # interlineado 
link-citations: yes         # citas linkeadas
# date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
date: "`r format(Sys.Date(), '%d %B %Y')`"
author:
# - name: Julio Iturra-Sanhueza
#   affiliation: University of Bremen
#   email: jiturra@uni-bremen.de
#   number: 1
# - name: Justin d'Ottawa
#   affiliation: University of Ottawa
#   number: 2
# - name: Pedro Torres
#   number: 1,2 
# Nota: Autores que comparten filiacion, poner el mismo number y declarar filiación una sola vez.  
# abstract: "Lorem ipsum dolor sit amet, consectetur adipisicing elit, sed do *eiusmod tempor* incididunt ut labore et dolore magna aliqua. Ut enimad minim veniam, quis nostrud exercitation ullamco laboris nisi ut aliquip ex ea commodo consequat."
output:
  bookdown::pdf_document2:
    template: null
    toc: false
    keep_tex: false
    pandoc_args:
      - --template=input/mytemplate.tex #custom template para usar autores con afiliacion  
  bookdown::html_document2:
    toc: yes
    code_folding: hide
    toc_float:
      collapsed: false
      smooth_scroll: false
    number_sections: false   
linkcolor: blue                         # enlaces y citas en color azul
bibliography: input/bib/rgroup-redist.bib     # bibliografia en bibtex
csl: input/bib/apa6.csl
editor_options:
  chunk_output_type: console            # en RStudio, mostrar output en consola
geometry: "left=2cm,right=2cm,top=3cm,bottom=3cm" # márgenes de página
header-includes:
  - \usepackage{times}           # Times New Roman
  - \usepackage{caption}
  - \captionsetup[figure, table]{labelfont={bf},labelformat={default},labelsep=period}
  - \usepackage{graphicx}
  - \usepackage{float}
  - \usepackage{booktabs}
  - \usepackage{longtable}
  - \usepackage{array}
  - \usepackage{multirow}
  - \usepackage{wrapfig}
  - \usepackage{float}
  - \usepackage{colortbl}
  - \usepackage{pdflscape}
  - \usepackage{tabu}
  - \usepackage{threeparttable}
---

@@

The response categories are  (1)"Never", (2)"Rarely", (3) "Sometimes", (4)"Often" and  (5)"Very often". As the indicators show an acceptable internal consistency ($\alpha$=.85), an index of the three items was created. Positive values indicate higher perceived isolation.
